Visibility Graph Analysis of the 2005-2015 Earthquake Sequence in Northern Iran

### 2016-05-31 results.tex
First complete draft

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure066.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:random}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent
The relationship between $b-value$ and $K-M$ slope for Azerbaijan and Alborz region, suggested the idea of similar tectonic activity in these zones, in contrast with the $b-value$. In other words, may $K-M$ slope is more robust and less sensitive than $b-value$. Adding the value of this study into two previous similar studies results improves the regression factor (increase from R=0.95 to R=0.958) and empower the idea of universal character of the relationship between the $b-value$ and the $k-M$ slope as \citet{Telesca2014} pointed out.

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 40 events as a window length. We analyzed the sensitivity of the results to the window size. Even though there is a very good similarity between the $K-M$ slope and $b-value$ in Alborz tectonic seismic region, there is no as good as fit for Azerbaijan Tectonic seismic region. The results indicate the fact that, $K-M$ slope may provide extra information about the seismic sequence of the region than the $b-value$.

The value of the K-M is increasing with increasing the magnitude. Fig yy shows the time vacation of the $K-M$ plot and $b-value$ for all tectonic seismic regions.

In general, In all regions the $b-value$ and $K-M$ slope considerably drops before  big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

Earthquake is a time dependent phenomenon, so studying the dynamic properties of the earthquake sequence is important to get different time dependent parameters.

 \citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude.

The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. In general, more number of samples in a window smooth the results.

 In this study with increasing window size we can see the same behavior as small window. Undoubtedly, larger window size will reduce the effect of

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:tc}
\end{figure}

>>>>

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.4]{figures/pdf/Figure06.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones for 200 random sequence. The numbers on the mean and standard deviation plots are coefficient of variations $(std/mean)$}
\label{fig:random}
\end{figure}

@@

\begin{figure} [ht]
\centering
\includegraphics[scale=0.3]{figures/pdf/Figure07.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:regression}
\end{figure}

\noindent 
Fig.\ref{fig:tc}  shows the variation of the $k-M$ slope and $b-value$ with time. Having lower number of event, we used 40 events as a window length with shift of one event between two successive window. There is a very good similarity between the $K-M$ slope and $b-value$ in all tectonic seismic regions. In general, In all regions the $b-value$ and $K-M$ slope considerably drop before big earthquakes. Dropping the $b-value$ before large earthquakes have been studied in many different region \citep[e.g.][]{Wyss2000,Wyss2006,Schorlemmer2005,Chan2012}

\noindent
\citet{Telesca2016} observed the decreasing of the $<Tc>$ before large earthquake of Western India earthquake sequence. Fig.~\ref{fig:tc} shows the time variation of $<Tc>$ in the study area. The decreasing of the $<Tc>$ for large earthquakes have been shown in the figure. \citet{Telesca2016} demonstrated that the decrement of $<Tc>$ before large earthquake are independent of window size and the threshold magnitude. The fluctuation of magnitude time series' topology properties (e.g. the $k-M$ slope and $<Tc>$) could be affected by the window size. Sharp changes in the VG parameters happens through small windows. Using higher number of samples in the window will reduce the temporal effects of small or moderate earthquakes and highlight the effects of big earthquakes, even though the behavior of the parameters in time and also before big earthquake are similar \citep{Telesca2016}. In general, more number of samples in a window smooth the results and highlight the effect of events with big magnitudes.

 \begin{figure} [ht]
\centering
\includegraphics[scale=0.34]{figures/pdf/Figure08.pdf} 
\caption{ Relationship between $K-M$ and $b-value$ of three Iranian tectonic seismic zones (this study) and two other studies of Mexican zones \citep{Telesca2013}, and Pannonia zones \citep{Telesca2014}. The dashed red line shows the regression line for data of  Mexican zones and Pannonia zones \citep{Telesca2014}, and the solid blue line shows the regression line for data of all regions (Mexican, Pannonian and North Iran)}
\label{fig:tc}
\end{figure}
